BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-09 tex/3-algorithms.tex
Minor
Solve some \cite TODOs.

% observations when working with blogs
Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts, often less than the total number of posts in blogs \cite{oita2010}. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.

@@

The Sørensen–Dice coefficient method operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:

@@

% into: algo 1 defined
The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortized} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

>>>>

% observations when working with blogs
Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.

@@

The Sørensen–Dice coefficient similarity algorithm operates by first building sets of pairs of adjacent characters, also knows as \emph{bigrams}, and then applying the \emph{quotient of similarity} formula:

@@

% into: algo 1 defined
The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% proof
With bigrams computed in this dynamic programming manner, the overall time to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortized} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

### 2013-12-09 tex/4-techniques.tex
Solve some \cite TODOs.

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
  \label{architecture}
\end{figure}

@@

% Distance-Weighted k-Nearest-Neighbor
The idea is to give a high priority to URLs which are believed to point to pages with links to blog post. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. To *lighten* our explanations we first introduce the following notation: let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Each time a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. The value of $L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.

@@

\TODO{To achieve this} property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

>>>>

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}
  \label{architecture}
\end{figure}

@@

% Distance-Weighted k-Nearest-Neighbor
The idea is to give a high priority to URLs which are believed to point to pages with links to blog post. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.

@@

To go in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator. By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

### 2013-12-09 tex/5-evaluation.tex
Solve some \cite TODOs.

Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor. Timing measurements used a single dedicated core with garbage collector disabled. The Git repository of this paper \cite{blogforever-crawler-publication} \TODO{cite blogforever-crawler-publication} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.

>>>>

Experiments were made on \emph{Debian GNU/Linux 7.2} with \emph{Python 2.7} on an \emph{Intel Core i7-3770 3.4 GHz} processor. Timing measurements used a single dedicated core with garbage collector disabled. The Git repository of this paper \cite{repositoryofthispaper} contains the necessary scripts and instructions to reproduce all evaluation experiments presented in this section.

### 2013-12-09 tex/6-conclusion-and-future-work.tex
Solve some \cite TODOs.

% Conclude the conclude
To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website. \TODO{cite \\https://github.com/OlivierBlanvillain/blogforever-crawler or http://blogforever.eu/ ?}.

>>>>

% Conclude the conclude
To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website \cite{blogforevercrawler}.
